|

### 2021-03-21 appendix/appendix.Rmd
appendix with theory begin

In this section, we present the @weingast1981political theoretical arguments behind the law of 1/n, and their rebuttal by @primo2008distributive. Many of the papers included in this meta-analysis also have their own version of why we need a refined version of the XXXX, but these two papers, in our view, present the most elementary theoretical argument

@@

XXXX PAREI AQUI

As the above condition suggests, the law of 1/n holds in specific situations. @primo2008distributive XXXX cost is when the suppose that we have a set of representatives, indexed in districts $i \in \{1, \cdots, n \}$.

@@

5. The estimation method used in the papers (variable `method`):
  - `OLS`: Ordinary-Least Squares in Cross-Sectional data.
  - `PANEL`: Time-Series Cross-Section models, with estimated fixed effects.
  - `IV`: Instrumental Variables models.
  - `RDD`: Regression Discontinuity Designs.

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
              tdist = TRUE,
              subset = dat$depvar2=='PCTGDP',
              slab = dat$authoryear)

@@

We have the following results for the meta-regressions of Expenditure as a Percentage of GDP:

1. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.

2. All other moderators remain insignificant.

@@

For all the coefficients, we have the following results:

1. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.

2. All other moderators remain insignificant.

@@

6. The estimation method used in the paper (OLS, PANEL, IV, or RDD).

>>>>

In this section, we present the @weingast1981political theoretical arguments behind the law of 1/n, and their rebuttal by @primo2008distributive. Many of the papers included in this meta-analysis also have their own version of why we need a refined version of the original law of 1/n, but these two papers, in our view, present the most elementary theoretical argument

@@

As the above condition suggests, the law of 1/n holds only in specific situations. @primo2008distributive advances the theory by considering other situations where the law may not hold, and also situations when a reverse prediction of the law of 1/n holds, i. e., larger legislatures leading to lower expenditures. 
Following @primo2008distributive, let $n$ be the number of districts, $m$ the number of citizens in each district, and $nm$ is the total population in the country. Consider a local public good that generates a per capita benefit, according to its size $x$ of $b(x, m) = x^\alpha m^{\beta-1}$, where $\beta$ is the degree of congestion of the public good, i. e. how much the addition of individuals reduce the benefits for other individuals (note that the lower the $\beta$, the higher the congestion). In terms of costs, consider a linear cost $C(x) = x$, and in terms of taxation, assume that the people in the district share taxes between their payments and the central government's. The degree that taxes are shared is denoted by $s$. Moreover, there is a deadweight loss of the taxes $\theta \geq 1$. The tax then becomes: $t = \left(\dfrac{(n – ns + s)x + (ns – s)X}{nm}\right)^\theta$. Collecting terms, the citizens receive the following net benefit of a project with size $x$:

\[
\pi = x^\alpha m^{\beta-1} - \left(\dfrac{(n – ns + s)x + (ns – s)X}{nm}\right)^\theta
\]

Maximizing this function, and solving for the symmetric Nash equilibrium where $x = X$ for all projects yield to the following optimal project size:

\[
x^* = \left[\left(\dfrac{\alpha}{\theta}\right)^{\dfrac{1}{\theta-\alpha}}\right]\left[\left(nm\right)^{\dfrac{\beta+\theta-1}{\theta - \alpha}}\right]\left[\left( \dfrac{n^{2-\beta-\theta}}{n-ns+s}\right)^{\dfrac{1}{\theta-\alpha}}\right]
\]

And in the graph below, we show simulations for $n$ varying from 10 to 20, holding constant $\beta = 0.35$, $\theta \in \{0.65, 0.75\}$, $s = 0.5$, $m = 100$, and $\alpha = 0.7$.

```{r, echo=FALSE, cache=TRUE, fig.align='center'}
xstar <- function(x, beta, theta, alpha = 0.7, s = 0.5, m = 10) {
  n = x
  a = (alpha/theta)^(1/(theta-alpha))
  b = (n*m)^((beta+theta-1)/(theta-alpha))
  c = ((n^(2-beta-theta))/(n-n*s+s))^(1/(theta-alpha))
  return (a*b*c)
}

curve(xstar(x, beta = 0.35, theta = 0.8), from = 10, to = 20,
      main = 'Increasing project size when varying legislature size \n (high deadweight losses)', xlab = 'Project Size', ylab = 'Number of Districts (legislature size)')
curve(xstar(x, beta = 0.35, theta = 0.5), from = 10, to = 20,
      main = 'Decreasing project size when varying legislature size \n (low deadweight losses)', xlab = 'Project Size', ylab = 'Number of Districts (legislature size)')
```

Therefore, there are possibilities for having the law of 1/n in the direction predicted by @weingast1981political, and in a reverse direction, as in @primo2008distributive. Here, we showed the variation changing only the deadweight losses, but there are many other theoretical reasons, such as the limiting power of the upper houses [@malhotra], the XXXX, and XXXX. Most of the literature after @weingast1981political, attempted to find the empirical complements to this original formulation.

@@

5. A institution design variable, with:
 - `Unicameral` (e.g., US Municipalities)
 - `Bicameral` (e.g., US States)
 - `Mixed` (e.g., countries with unicameral and bicameral in the same dataset).

6. The estimation method used in the papers (variable `method`):
  - `OLS`: Ordinary-Least Squares in Cross-Sectional data.
  - `PANEL`: Time-Series Cross-Section models, with estimated fixed effects.
  - `IV`: Instrumental Variables models.
  - `RDD`: Regression Discontinuity Designs.

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+method,
              test = "knha",
              tdist = TRUE,
              subset = dat$depvar2=='PCTGDP',
              slab = dat$authoryear)

@@

All moderators are insignificant in the meta-regressions of Expenditure as a Percentage of GDP.

@@

Even for all the coefficients, all moderators remain insignificant.

@@

6. The institution design: whether the legislature in the analysis is unicameral, bicameral, or mixed.

7. The estimation method used in the paper (OLS, PANEL, IV, or RDD).
